\chapter{REFERENCES}
\begin{enumerate}  
\item WebMate: A Tool for Testing Web 2.0 Applications, Authors: Valentin Dallmeier,Martin Burger, Tobias Orth, Andreas Zeller Journal: JSTools'12, June 13, 2012, China.
  \newblock
\item Model-Based Vulnerability Testing for Web Applications, Conference: Software Testing,Verification and Validation Workshops (ICSTW), 2013 IEEE Sixth International Conference on Authors: Franck Lebeau, Bruno Legeard, Fabien Peureux.
\newblock
\item Search-based security testing of web applications. Authors: Julian Thomé, Andreas Zeller, Alessandra Gorla. Conference: SBST 2014 Proceedings of the 7th International Workshop on Search-Based Software Testing.
\item Crawling AJAX by Inferring User Interface State Changes Authors: Arie van Deursen, Ali Mesbah, Engin Bozdag. Conference: Web Engineering, 2008. ICWE '08. Eighth International Conference
\item A Crawljax Based Approach to Exploit Traditional Accessibility Evaluation Tools for AJAX Applications. Authors: F. Ferrucci1 , F. Sarro1 , D. Ronca1 , S. Abrahao2. Journal: Information Technology and Innovation Trends in Organizations, May 2011.
\item Automatic Creation of SQL Injection and Cross-Site Scripting Attacks. Authors: Adam Kiezun ˙ ,
Philip J. Guo , Karthick Jayaraman , Michael D. Ernst
\item A Survey on Model-based Testing Approaches: A Systematic Review. Authors: Arilo C. Dias, Neto Rajesh, Subramanyan
 Marlon Vieira, Guilherme H. Travassos
\item OWASP Top10 Security vulnerabilities. \\
https://www.owasp.org/index.php/Top\_10-2017\_Top\_10
\item Mechanize Browser API Documentation.\\
http://mechanize.readthedocs.io/en/latest/browser\_api.html
\item Beautiful Soup HTML Parser Documentation.\\
https://www.crummy.com/software/BeautifulSoup/bs4/doc/
\end{enumerate}